### 2015-07-30 bioc192/intro.tex
added graphics

Please DO NOT send this book around, especially to the HSFY students, unless you have asked the author (i.e. me) if you could do so.
All rights reserved.
No commercial reproduction, adaptation, distribution or transmission (and any other legal crap people put on their books) of this book is permitted without the written permission of the author (Riku Takei).

>>>>

Please DO NOT send this book around, especially to the HSFY students, unless you have asked the author (i.e. me) if you could do so.
All rights reserved.
No commercial reproduction, adaptation, distribution or transmission (and any other legal crap people put on their books) of this book is permitted without the written permission of the author.

### 2015-07-30 bioc192/lect01.tex
making separate lecture files
added graphics

\documentclass[a4paper, 12pt]{report}

\usepackage{graphicx}
\usepackage[utf8]{inputenc}

\newcommand{\HRule}{\rule {\linewidth}{0.5mm}}

\newcommand{\mychapter}[2]{
    \setcounter{chapter}{#1}
    \setcounter{section}{0}
    \chapter*{#2}
    \addcontentsline{toc}{chapter}{#2}
}

\begin{document}

\input{./title/title.tex}

\tableofcontents
\newpage

\mychapter{0}{Introduction}

\mychapter{1}{Lecture 1}
\section{Protein}

@@

Amino acids are the building blocks of a protein.
Proteins are made from multiple amino acids joined together as a long polypeptide chain, which in turn folds into a certain structure (ref to diff. chapter).

There are 20 amino acids in our cells that make up the proteins (insert image of 20 aa).
All of these 20 amino acids have an amino group (--NH$_3$ group), a carboxyl group (--COOH group), a hydrogen atom, and a variable side chain (--R group) attached to the central carbon atom (C$_{\alpha}$) (insert image of amino acid structure).
Due to the variable side chains, all amino acids except glycine are chiral, meaning that they cannot be mirrored (and hence have two forms: D-- and L-- amino acids).
The reason why glycine is the only amino acid that is achiral is because the glycine side chain group is just a hydrogen atom.

@@

@@

@@

\mychapter{2}{Lecture 2}

\section{Bond Rotation}

\end{document}

>>>>

\section{Protein}

@@

Amino acids are the building blocks of a protein.
Proteins are made from multiple amino acids joined together as a long polypeptide chain, which in turn folds into a certain structure (see Lecture 2).

There are 20 amino acids in our cells that make up the proteins.
All of these 20 amino acids have an amino group (--NH$_3$ group), a carboxyl group (--COOH group), a hydrogen atom, and a variable side chain (--R group) attached to the central carbon atom (C$_{\alpha}$).
Due to the variable side chains, all amino acids except glycine are chiral, meaning that they cannot be mirrored (and hence have two forms: D-- and L-- amino acids).
The reason why glycine is the only amino acid that is achiral is because the glycine side chain group is just a hydrogen atom.

\includegraphics[width=\textwidth]{aastructure}

@@

\includegraphics[width=\textwidth]{20aa}

@@

\begin{center}
\includegraphics[width=0.8\textwidth]{aapka}
\end{center}

@@

\begin{center}
\includegraphics[width=\textwidth]{amidebond}
\end{center}
